### 2016-03-11 manuscript.Rnw
Update cat_tree text to reflect new trees in OTL :joy:

Currently only one study focused on this family is available from OTL, and a
single tree is associated with it. We can then retrieve the study and tree
identifiers, and pass them to the function \texttt{get\_study\_tree} to have the
tree in memory:

>>>>

Currently there are seven studies focused on this family available from OTL, and a
single tree is associated with each one. We can then retrieve the study and tree
identifiers associated with the first of these studies, and pass them to the 
function \texttt{get\_study\_tree} to have the tree in memory:
